---
title: "Lab 10 - Grading the professor"
author: "Thomas Huang"
date: "2026-03-26"
output: github_document
---

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab10.html).

## Load Packages and Data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)

data(evals)
?evals
```

# Part 1
## Exercise 1

By looking at the histogram and the descriptives, the distirbution is left skewed. In general, the students are generous.
```{r exercise1_code}
psych::describe(evals$score)

ggplot(evals, aes(x = score)) +
  geom_histogram()
```

## Exercise 2

It seems that there is a positive relationship between the two variables. But there is also a lot of noise.
```{r exercise2_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_point()
```

## Exercise 3

This function fixes stacked or overlapped observations, which gives a better visualization of number of observations, density of observations, and noise. One might be mislead by the last plot because it fails to visualize lots of noise in the data.
```{r exercise3_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter()
```

# Part 2
## Exercise 1
```{r}

```

## Hint

For Exercise 12, the `relevel()` function can be helpful!
