---
title: "Lab 10 - Grading the professor"
author: "Thomas Huang"
date: "2026-03-26"
output: github_document
---

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab10.html).

## Load Packages and Data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)

data(evals)
?evals
```

# Part 1
## Exercise 1

By looking at the histogram and the descriptives, the distirbution is left skewed. In general, the students are generous.
```{r exercise1_code}
psych::describe(evals$score)

ggplot(evals, aes(x = score)) +
  geom_histogram()
```

## Exercise 2

It seems that there is a positive relationship between the two variables. But there is also a lot of noise.
```{r exercise2_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_point()
```

## Exercise 3

This function fixes stacked or overlapped observations, which gives a better visualization of number of observations, density of observations, and noise. One might be mislead by the last plot because it fails to visualize lots of noise in the data.
```{r exercise3_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter()
```

# Part 2
## Exercise 1

Fitted regression equation:
$$\hat{y} = 3.88034 + 0.06664x$$

This equation suggests that a one-point increase in beauty predicts a 0.06664-point increase in course evaluation.
```{r}
m_bty <- lm(evals$score ~ evals$bty_avg)
summary(m_bty)
```

## Exercise 2

```{r}
# Visualize the regression lines
evals$score_p <- predict(m_bty, newdata = evals)

ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_line(aes(y = score_p), color = "red") + 
  labs(x = "Beauty", y = "Score") +
  theme_minimal()
```

## Exercise 3

The scores do not much with beauty ratings. That is, a one-point increase in beauty predicts a 0.06664-point increase in course evaluation scores. 

The intercept represents the avergae course evaluation scores of professors with a beauty rating of zero. It is more of a mathematical artifact in this case because beauty is rated on a scale from 1 to 10. Nobody will get a zero in beauty ratings. The meaningful minimum of beauty rating is 1.

The $R^2$ is .035. This indicates beauty ratings explain 3.5% of the variance in course evaluation scores. This is a minor piece of the story.

I assume there will be a lot of uncertainty around the line. At this stage, the substaintial shade may couse the confusion that the model is strong and certain.

# Part 3
## Exercise 1

The reference level is female. The mean difference in evaluation scores indicates that the mean score male professor is 0.142 point higher than that of female professors.
```{r}
m_gen <- lm(score ~ gender, data = evals)
tidy(m_gen)
```

```{r}
evals$rank_relevel <- relevel(evals$rank, ref = "tenure track")
evals$tenure_eligible <- ifelse(evals$rank == "teaching", "no", "yes")
```

## Exercise 2

```{r}
m_rank <- lm(score ~ rank, data = evals)
m_relevel <- lm(score ~ rank_relevel, data = evals)
m_tenure <- lm(score ~ tenure_eligible, data = evals)
```

## Exercise 3

Teaching faculty receives higher scores. Tenured faculty receoives lower scores.
```{r}
summary(m_rank)
summary(m_relevel)
summary(m_tenure)
```

## Exercise 4

The $R^2$'s are .012, .012, and .012. Rank does not explain much.

# Part 4

```{r}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
summary(m_bty_gen)
```

## Exercise 1

The beauty slope has increased, or become larger in value.

## Exercise 2

The gender slope is still statistically significant. So, yes.

## Exercise 3

The adjusted $R^2$ is .055. Having gender in the model is helpful.

## Exercise 4

Within the same rank of faculty, a one-point increase in beauty rating predicts a 0.68-point increase in course evaluation score. Holding beauty rating constant, tenure-track and tenured faculty have lower course evaluation compared to teaching faculty.
```{r}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
summary(m_bty_rank)
```

# Part 5
## Exercise 1

I think cls_level is the worst predictor

## Exercise 2

The slope is not statistically significant.
```{r}
m_cls_level <- lm(score ~ cls_level, data = evals)
summary(m_cls_level)
```

## Exercise 3

I would not include cls_did_eval. This is cls_perc_eval on a different scale. They are mathematically equivalent in predictive power.

## Exercise 4

```{r}
full <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval + cls_students + cls_level + cls_profs + cls_credits + bty_avg, data = evals)
summary(full)
```

## Exercise 5

This is the best model: score ~ ethnicity + gender + language + age + cls_perc_eval + cls_credits + bty_avg. The regression equation is
$$\hat{y} = 3.446967 -  0.204710EthnicityMinority - 0.184780GenderFemale - 0.161463LanguageNonEnglish - 0.005008Age + 0.005094ClsPercEval + 0.515065ClsCreditsOneCredit + 0.064996BtyAvg$$

```{r}
evals$ethnicity <- relevel(evals$ethnicity, ref = "not minority")
evals$gender <- relevel(evals$gender, ref = "male")
evals$language <- relevel(evals$language, ref = "english")
evals$cls_credits <- relevel(evals$cls_credits, ref = "multi credit")

best <- lm(score ~ ethnicity + gender + language + age + cls_perc_eval + cls_credits + bty_avg, data = evals)
summary(best)
```

## Exercise 6

Holding everything else constant, a one-point increase in beauty rating predicts a 0.064996-point increase in teaching evaluation score. Holding everything else constant, female faculty's average evaluation score is 0.184780 lower than that of male faculty.

## Exercise 7

A one-credit class with a high percentage of students completing the evaluation taught by a professor who is white, male, educated in an English-speaking school, young, and visually appealing in UT Austin.

## Exercise 8

I am not comfortable generalizing your conclusions to apply to professors generally. These conclusions are sad. Certain demographic features of a professor explains a big part of variance in teaching evaluation. In other words, course evaluation scores are not totally about instructional quality, but also concerns whether the professor fits certain demographic features.


