---
title: "Lab 10 - Grading the professor"
author: "Thomas Huang"
date: "2026-03-26"
output: github_document
---

Here is a link to the [lab instructions](https://datascience4psych.github.io/DataScience4Psych/lab10.html).

## Load Packages and Data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)

data(evals)
?evals
```

# Part 1
## Exercise 1

By looking at the histogram and the descriptives, the distirbution is left skewed. In general, the students are generous.
```{r exercise1_code}
psych::describe(evals$score)

ggplot(evals, aes(x = score)) +
  geom_histogram()
```

## Exercise 2

It seems that there is a positive relationship between the two variables. But there is also a lot of noise.
```{r exercise2_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_point()
```

## Exercise 3

This function fixes stacked or overlapped observations, which gives a better visualization of number of observations, density of observations, and noise. One might be mislead by the last plot because it fails to visualize lots of noise in the data.
```{r exercise3_code}
ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter()
```

# Part 2
## Exercise 1

Fitted regression equation:
$$\hat{y} = 3.88034 + 0.06664x$$

This equation suggests that a one-point increase in beauty predicts a 0.06664-point increase in course evaluation.
```{r}
m_bty <- lm(evals$score ~ evals$bty_avg)
summary(m_bty)
```

## Exercise 2

```{r}
# Visualize the regression lines
evals$score_p <- predict(m_bty, newdata = evals)

ggplot(evals, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_line(aes(y = score_p), color = "red") + 
  labs(x = "Beauty", y = "Score") +
  theme_minimal()
```

## Exercise 3

The scores do not much with beauty ratings. That is, a one-point increase in beauty predicts a 0.06664-point increase in course evaluation scores. 

The intercept represents the avergae course evaluation scores of professors with a beauty rating of zero. It is more of a mathematical artifact in this case because beauty is rated on a scale from 1 to 10. Nobody will get a zero in beauty ratings. The meaningful minimum of beauty rating is 1.

The $R^2$ is .035. This indicates beauty ratings explain 3.5% of the variance in course evaluation scores. This is a minor piece of the story.

I assume there will be a lot of uncertainty around the line. At this stage, the substaintial shade may couse the confusion that the model is strong and certain.

# Part 3

## Hint

For Exercise 12, the `relevel()` function can be helpful!
